Network based multifactorial modelling microRNA-target interaction.

### 2019-12-20 NAR_form_article.Rmd
add refer to Figure S10

Additionally, miRNA:gene expression dataset which was integrated via miRTarBase [@chou2017mirtarbase] was analysed in mean of perturbation efficiency to determine crucial genes on the network. We have observed that one miRNA and 297 genes have high perturbation efficiency, when we ran our model with more than 17% efficiency on target expression. The miRNA, miR-10b was investigated via HMDD database [@huang2018hmdd] and was found as metastatic biomarker. The genes with high perturbation efficiency were analysed via eDGAR, a database of Disease-Gene Associations with annotated relationships among genes [@babbi2017edgar] that supplies different observations about crucial genes such as direct physical interactions, other shared genes with these interactions, protein-protein interactions, GO terms etc.  With our model, we obtained 3 (TP53, BRCA1, AKT1) of 27 critical breast cancer genes and these genes show direct physical interaction with 21 genes. 33 shared genes which are observed on these direct interactions were also found in our effective perturbation elements. We have obtained 7 (KLF4, TP53, BRCA1, CREB, ID4, GATA3, CTBP1) transcription factors (TFs) that are common in 44 critical TFs which are provided by eDGAR dataset. 44 of regulated genes via these TFs were found in our highly effective genes. it has been observed that these genes cover 22.5% of 297 perturbation-effective genes.

>>>>

Additionally, miRNA:gene expression dataset which was integrated via miRTarBase [@chou2017mirtarbase] was analysed in mean of perturbation efficiency to determine crucial genes on the network. We have observed that one miRNA and 297 genes have high perturbation efficiency, when we ran our model with more than 17% efficiency on target expression. The miRNA, miR-10b was investigated via HMDD database [@huang2018hmdd] and was found as metastatic biomarker. The genes with high perturbation efficiency were analysed via eDGAR, a database of Disease-Gene Associations with annotated relationships among genes [@babbi2017edgar] that supplies different observations about crucial genes such as direct physical interactions, other shared genes with these interactions, protein-protein interactions, GO terms etc.  With our model, we obtained 3 (TP53, BRCA1, AKT1) of 27 critical breast cancer genes and these genes show direct physical interaction with 21 genes (Figure S10). 33 shared genes which are observed on these direct interactions were also found in our effective perturbation elements. We have obtained 7 (KLF4, TP53, BRCA1, CREB, ID4, GATA3, CTBP1) transcription factors (TFs) that are common in 44 critical TFs which are provided by eDGAR dataset (Figure S10). 44 of regulated genes via these TFs were found in our highly effective genes. it has been observed that these genes cover 22.5% of 297 perturbation-effective genes.
